Examining FDR correction issue in clusterProfiler - RNA-seq example

### 2024-09-12 analysis/analyse_rnaseq2.Rmd
add means to boxplot

par(mar = c(5.1, 8.1, 4.1, 2.1))
library(beeswarm)
boxplot(res3d,horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05")
beeswarm(res3d,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)

res3d1 <- res3d + 1
boxplot(res3d1,log="x",horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(res3d1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)

@@

boxplot(res3d1,log="x",horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(res3d1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)

>>>>

par(mar = c(5.1, 8.1, 4.1, 2.1))
library(beeswarm)
boxplot(res3d,horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05")
beeswarm(res3d,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(res3d)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)

res3d1 <- res3d + 1
boxplot(res3d1,log="x",horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(res3d1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(res3d1)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)

@@

boxplot(res3d1,log="x",horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(res3d1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(res3d1)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)
